An Introduction to Return Oriented Programming

### 2023-02-17 paper.tex
changes

\section{Conclusion}
As it has been demonstrated Return Oriented Programming is a powerful exploitation technique which should be taken seriously. As we were able to see the only way to make a binary relatively safe is to compile it as 64 Bit with stack canaries, bounds checking and ASLR enabled, though even then side channel attacks, bugs and bruteforcing based on a poor entropy pool may make an attack possible. Replacing or patching vulnerable devices is very important and more research on this topic paired with direct action in systems design may be necessary to keep up with black-hats.
%%%% 8. BILBIOGRAPHY %%%%
\bibliographystyle{alpha}
\bibliography{refs}
%%%% NOTES
% - Download abbrev3.bib and crypto.bib from https://cryptobib.di.ens.fr/
% - Use bilbio.bib for additional references not in the cryptobib database.
%   If possible, take them from DBLP.
\end{document}

>>>>

\section{Conclusion}
As it has been demonstrated Return Oriented Programming is a powerful exploitation technique which should be taken seriously. From the research surrounding the attacking technique and protection mechanisms the only way to make the binary relatively safe is to compile it as 64 Bit executable with stack canaries, bounds checking and ASLR enabled, though even then side channel attacks, bugs and bruteforcing based on a poor entropy pool may make an attack possible. Replacing or patching vulnerable devices is very important and more research on this topic paired with direct action in systems design may be necessary to keep up with black-hats.
%%%% 8. BILBIOGRAPHY %%%%
\bibliographystyle{alpha}
\bibliography{refs}
%%%% NOTES
% - Download abbrev3.bib and crypto.bib from https://cryptobib.di.ens.fr/
% - Use bilbio.bib for additional references not in the cryptobib database.
%   If possible, take them from DBLP.
\end{document}
